Proving Logical Atomicity using Lock Invariants\thanks{Supported by the National Science Foundation via grant \#1811894.}

### 2022-05-05 concurrency/ASL 2022/Verification of Concurrent Binary Search Tree.tex
Tune the layout of the figures.

\begin{figure}[htb]
\centering
\forestset{
   lab/.style={
        label={[anchor=west, scale=0.75] north east:#1},
    },
}
\begin{forest}
for tree={
    grow=south,
    circle, draw, minimum size=3ex, inner sep=1pt,
    s sep=3mm, l sep=0mm
        }
    % my label/.style={
        % label={[anchor=south west] north east:#1},
    % },
    [ 20, tikz={\node[right=0pt of .north east, scale=0.75]  {$(-\infty,\infty)$};}
        [15, tikz={\node[left=0pt of .north west, scale=0.75]  {$(-\infty,20)$};}]
        [30, tikz={\node[right=0pt of .north east, scale=0.75]  {$(20,\infty)$};}
            [25, tikz={\node[left=0pt of .north west, scale=0.75]  {$(20,30)$};}]
            [50, tikz={\node[right=0pt of .north east, scale=0.75]  {$(30,\infty)$};}
                [45, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,50)$};}
                    [40, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,45)$};}
                        [35, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,40)$};}
                            [, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,35)$};}]
                            [, tikz={\node[right=0pt of .north east, scale=0.75]  {$(35,40)$};}]
                        ]
                        [,no edge, draw=none]
                    ]
                    [,no edge, draw=none]
                ]
                [,no edge, draw=none]
            ]
        ]
    ]
\end{forest}
\caption{A BST with each node labeled with its range}
\label{range_bst}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{forest}
for tree={
    grow=south,
    circle, draw, minimum size=3ex, inner sep=1pt,
    s sep=3mm, l sep=0mm
        }
    [, phantom, for children={fit=band}, s sep+=20mm,
         before drawing tree={%
          tikz+={%
            \node (a) [inner sep=0pt, fit=(!1) (!1L) (!1F)] {};
            \node (b) [inner sep=0pt, fit=(!l) (!lL) (!lF)] {};
            \node [anchor=south] at ($(a.east)!1/2!(b.west)$) {$\Longrightarrow\quad$};
          },
        },
        [ 20, tikz={\node[right=0pt of .north east, scale=0.75]  {$(-\infty,\infty)$};}
            [15, tikz={\node[left=0pt of .north west, scale=0.75]  {$(-\infty,20)$};}]
            [30, tikz={\node[right=0pt of .north east, scale=0.75]  {$(20,\infty)$};}
                [25, tikz={\node[left=0pt of .north west, scale=0.75]  {$(20,30)$};}]
                [50, tikz={\node[right=0pt of .north east, scale=0.75]  {$(30,\infty)$};}
                    [45, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,50)$};}
                        [40, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,45)$};}
                            [35, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,40)$};}
                                [, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,35)$};}]
                                [, very thick, tikz={\node[right=0pt of .north east, scale=0.75]  {$(35,40)$};} %weirdly lopsided
                                ]
                            ]
                            [,no edge, draw=none]
                        ]
                        [,no edge, draw=none]
                    ]
                    [,no edge, draw=none]
                ]
            ]
        ]
        [ 20, tikz={\node[right=0pt of .north east, scale=0.75]  {$(-\infty,\infty)$};}
            [15, tikz={\node[left=0pt of .north west, scale=0.75]  {$(-\infty,20)$};}]
            [30, tikz={\node[right=0pt of .north east, scale=0.75]  {$(20,\infty)$};}
                [25, tikz={\node[left=0pt of .north west, scale=0.75]  {$(20,30)$};}]
                [50, tikz={\node[right=0pt of .north east, scale=0.75]  {$(30,\infty)$};}
                    [45, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,50)$};}
                        [40, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,45)$};}
                            [35, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,40)$};}
                                [, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,35)$};}]
                                [38, very thick, tikz={\node[right=0pt of .north east, scale=0.75]  {$(35,40)$};}
                                    []
                                    []
                                ]
                            ]
                            [,no edge, draw=none]
                        ]
                        [,no edge, draw=none]
                    ]
                    [,no edge, draw=none]
                ]
            ]
        ]
    ]
\end{forest}
\caption{Adding a new key (38) at a leaf}
\label{extract_insert}
\end{figure}

@@

    s sep=3mm

@@

            \node (a) [inner sep=0pt, fit=(!1) (!1L) (!1F)] {};
            \node (c) [inner sep=0pt, fit=(!l) (!lL) (!lF)] {};

@@

            \node [anchor=south] at ($(a.east)!1/3!(b.west)$) {$\Longrightarrow\quad$};
            \node [anchor=south] at ($(b.east)!1/2!(c.west)$) {$\Longrightarrow$};

>>>>

\begin{figure}[htb]
\centering
%% \forestset{
%%    lab/.style={
%%         label={[anchor=west, scale=0.75] north east:#1},
%%     },
%% }
\begin{forest}
for tree={
  calign=fixed edge angles,
  calign angle=65,
  circle, draw, minimum size=3ex, inner sep=1pt, l sep=0, l=0,
%%     s sep=3mm, l sep=0mm
        }
    % my label/.style={
        % label={[anchor=south west] north east:#1},
    % },
    [ 20, tikz={\node[right=0pt of .north east, scale=0.75]  {$(-\infty,\infty)$};}
        [15, tikz={\node[left=0pt of .north west, scale=0.75]  {$(-\infty,20)$};}]
        [30, tikz={\node[right=0pt of .north east, scale=0.75]  {$(20,\infty)$};}
            [25, tikz={\node[left=-2pt of .west, scale=0.75]  {$(20,30)$};}]
            [50, tikz={\node[right=0pt of .north east, scale=0.75]  {$(30,\infty)$};}
                [45, tikz={\node[right=0pt of .south east, scale=0.75]  {$(30,50)$};}
                    [40, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,45)$};}
                        [35, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,40)$};}
                            [, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,35)$};}]
                            [, tikz={\node[right=0pt of .north east, scale=0.75]  {$(35,40)$};}]
                        ]
                        [,no edge, draw=none]
                    ]
                    [,no edge, draw=none]
                ]
                [,no edge, draw=none]
            ]
        ]
    ]
\end{forest}
\caption{A BST with each node labeled with its range}
\label{range_bst}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{forest}
  for tree={
    calign=fixed edge angles,
    calign angle=50,
    circle, draw, minimum size=3ex, inner sep=1pt,
    l=0, l sep=0.1em }
    [, phantom, for children={fit=band}, s sep+=10mm,
         before drawing tree={%
          tikz+={%
            \node (a) [inner sep=0pt, fit=(!1) (!1ll) (!1ll1111)] {};
            \node (b) [inner sep=0pt, fit=(!l) (!lll111l) (!l1)] {};
            \node [anchor=south] at ($(a.east)!1/2!(b.west)$) {{\large$\Longrightarrow$}};
          },
        },
        [ 20, tikz={\node[right=0pt of .north east, scale=0.75]  {$(-\infty,\infty)$};}
            [15, tikz={\node[left=0pt of .north west, scale=0.75]  {$(-\infty,20)$};}]
            [30, tikz={\node[right=0pt of .north east, scale=0.75]  {$(20,\infty)$};}
                [25, tikz={\node[left=-2pt of .west, scale=0.75]  {$(20,30)$};}]
                [50, tikz={\node[right=0pt of .north east, scale=0.75]  {$(30,\infty)$};}
                    [45, tikz={\node[right=0pt of .south east, scale=0.75]  {$(30,50)$};}
                        [40, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,45)$};}
                            [35, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,40)$};}
                                [, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,35)$};}]
                                [, very thick, tikz={\node[right=0pt of .north east, scale=0.75]  {$(35,40)$};} %weirdly lopsided
                                ]
                            ]
                            [,no edge, draw=none]
                        ]
                        [,no edge, draw=none]
                    ]
                    [,no edge, draw=none]
                ]
            ]
        ]
        [ 20, tikz={\node[right=0pt of .north east, scale=0.75]  {$(-\infty,\infty)$};}
            [15, tikz={\node[left=0pt of .north west, scale=0.75]  {$(-\infty,20)$};}]
            [30, tikz={\node[right=0pt of .north east, scale=0.75]  {$(20,\infty)$};}
                [25, tikz={\node[left=-2pt of .west, scale=0.75]  {$(20,30)$};}]
                [50, tikz={\node[right=0pt of .north east, scale=0.75]  {$(30,\infty)$};}
                    [45, tikz={\node[right=0pt of .south east, scale=0.75]  {$(30,50)$};}
                        [40, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,45)$};}
                            [35, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,40)$};}
                                [, tikz={\node[left=0pt of .north west, scale=0.75]  {$(30,35)$};}]
                                [38, very thick, tikz={\node[right=0pt of .north east, scale=0.75]  {$(35,40)$};}
                                    []
                                    []
                                ]
                            ]
                            [,no edge, draw=none]
                        ]
                        [,no edge, draw=none]
                    ]
                    [,no edge, draw=none]
                ]
            ]
        ]
    ]
\end{forest}
\caption{Adding a new key (38) at a leaf}
\label{extract_insert}
\end{figure}

@@

    s sep=3mm, l sep=0

@@

            \node (a) [inner sep=0pt, fit=(!1) (!1ll) (!1l1ll)] {};
            \node (c) [inner sep=0pt, fit=(!l) (!ll) (!ll111)] {};

@@

            \node [anchor=south] at ($(a.east)!2/5!(b.west)$) {$\Longrightarrow$};
            \node [anchor=south] at ($(b.east)!3/5!(c.west)$) {$\Longrightarrow$};
